Curiosity-Driven Development of Tool Use Precursors: a Robotic Model

### 2016-01-30 cogsci2016/paper.tex
intro

	The understanding of tool use development in young children is one of the key question for the more general understanding of the ontogeny of human cognition.
	Indeed, a series of abilities are progressively developed from the simplest reaching movements of the arms through more dexterous manipulation of a spoon, towards advanced control of multiple interacting objects.
	The latter shows an understanding of shapes, forces and other physical properties that can be recruited for mental transformations and planning operations which are pillars of human cognition.
	Children's development has first been described as staircase-like successive stages in which all children go through \cite{piaget1952origins}.
	More recently, a different view was developed \cite{siegler1996emerging} describing variability among children's developmental paths and in a child's set of current methods to solve a same task (called overlapping waves). 
	This applies in particular to the development of tool use precursors, which can be described as three consecutive and overlapping stages of behaviours \cite{guerin2013survey}: 
	behaviours without objects, behaviours with a single object, and behaviours with several interacting objects.
	A study of free manipulative play \cite{fenson1976developmental} shows that play at $7$ months was mostly composed of tactile and visual examination and mouthing of one object, 
	but simple relational acts of banging two objects together was already common.
	Later at $13\frac{1}{2}$ months, another study reveals that most children instead prefer to explore the relationships
	among objects \cite{Zelazo198095}.

>>>>

	The understanding of tool use development in young children is one of the key question for the more general understanding of the ontogeny of human cognition.
	Indeed, a series of abilities are progressively developed from the simplest reaching movements of the arms through more dexterous manipulation of a spoon, towards advanced control of multiple interacting objects.
	The latter shows an understanding of shapes, forces and other physical properties that can be recruited for mental transformations and planning operations which are pillars of human cognition.
	Children's development has first been described as staircase-like successive stages in which all children go through \cite{piaget1952origins}.
	More recently, a different view was developed \cite{siegler1996emerging} describing variability among children's developmental paths and in a child's set of current methods to solve a same task. 
	This applies in particular to the development of tool use precursors, which can be described as three consecutive and overlapping stages of behaviours \cite{guerin2013survey}: 
	behaviours without objects, behaviours with a single object, and behaviours with several interacting objects.
	A study of free play \cite{Zelazo198095} shows that at $9\frac{1}{2}$ months play is mostly composed of tactile examination, waving, banging and mouthing of a single object, 
	but that simple relational acts of banging two objects together is already common.
	Later at $13\frac{1}{2}$ months, the study reveals that most children instead prefer to explore the relationships
	among objects, but still show behaviors of the previous phase. 
	Furthermore, they show that this overlapping phases pattern averaged across children is also present in a longitudinal study of a single child.
